---
title: "STAT 184 Homework Exercises" 
subtitle: "DataComputing Chapter 7"
author: "eric weah"
output: html_notebook
---

## Assigned Exercises

- DC Chapter 7 Exercises: 7.1-7.6

## Front Matter

```{r}
# clean up workspace environment
rm(list = ls())

# all packages used for the assignment
library(mosaic)
library(tidyverse)
library(babynames)
library(DataComputing)
```



## Chapter 7 Exercises

### Problem 7.1

### problem 7.2
a.) The variable first should not be in quotes

b.) Summerise has not been defined, so it cannot use tmp as a argument

c.) The argument in summarise should be tmp

### problem 7.3
1.) There are 80101 cases

2.) Top 5 candidates are Betsy H, Don S, Mark A, Jackie C, and a undervote.

3.) There are 834 in first choice, 10598 in second choice and 19219 in the third choice.

4.)the top 3 combos of first vote selection is "ABDUL M RAHAMAN THE ROCK" 3 times. The top 3 combos second vote selection is a undervote, "ABDUL M RAHAMAN THE ROCK" and "Betsy Hodges".

5.) P-06 has the largest amount of ballots with 9711.

### problem 7.5
a.) The VoterData_A only has two cases consisting of first and second

b.)A case represents the total calculated

c.) A case represents the first and second varibles similar to VoterData_A

d.) The group_by should come before the summarise so it can read the vriables of first.

### problem 7.6
1.)
```{r}
ggplot(data=ZipGeography,aes(x=LandArea,y=Population))+geom_point()+aes(colour=State)
```
2.)
```{r}
 ggplot()
  + geom_polygon( data=ZipGeography, 
          aes(x=population, y=State, fill = population/1000000), 
          color="white", size = 0.2) 

```